$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-05 paper/e6ssm-tuning-paper.tex
Added two-loop beta for m_{H_d}^2, fixed some typos in two-loop beta for m_{H_u}^2

\beta_{m_{H_d}^2}^{(2)}&=,\label{eq:USSMmHd2BetaTwoLoop}\\

@@

&{}+2Q_2Q_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_2Q_{H'}^2m_{H'}^2+\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2\nonumber\\

>>>>

\beta_{m_{H_d}^2}^{(2)}&=-36y_b^4\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2\right )-12y_\tau^4\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2\right )-72y_b^2a_b^2-24y_\tau^2a_\tau^2\nonumber\\
&{}-6y_t^2y_b^2\left ( m_{H_d}^2+m_{H_u}^2+2m_{Q3}^2+m_{u3}^2+m_{d3}^2\right )-6\left ( y_t a_b+y_ba_t\right )^2\nonumber\\
&{}-4\lambda^4\left ( m_{H_d}^2+m_{H_u}^2+m_S^2\right )-8\lambda^2a_\lambda^2-\lambda^2\sum_{i=1}^3\left [ 4\lambda_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{H_i^d}^2\right.\right.\nonumber\\
&{}\left.\left.+m_{H_i^u}^2\right )+6\kappa_i^2\left ( m_{H_d}^2+m_{H_u}^2+2m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )\right ]-\sum_{i=1}^3\left [ 4\left ( \lambda_i a_{\lambda}+\lambda a_{\lambda_i}\right )^2\right.\nonumber\\
&{}\left.+6\left ( \kappa_ia_\lambda+\lambda a_{\kappa_i}\right )^2\right ]-6\lambda^2y_t^2\left ( m_{H_d}^2+2m_{H_u}^2+m_S^2+m_{Q3}^2+m_{u3}^2\right )-6\left ( \lambda a_t+y_ta_\lambda\right )^2\nonumber\\
&{}+32g_3^2y_b^2\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_3^2\right )+32g_3^2\left ( a_b^2-2y_ba_bM_3\right )\nonumber\\
&{}+\frac{6}{5}g_1^2y_t^2\left ( 3m_{H_u}^2+m_{Q3}^2-4m_{u3}^2\right )-\frac{2}{5}g_1^2y_b^2\left ( 11m_{H_d}^2-m_{Q3}^2-4m_{d3}^2+4M_1^2\right )\nonumber\\
&{}-\frac{4}{5}g_1^2\left ( a_b^2-2y_ba_bM_1\right )+\frac{6}{5}g_1^2y_\tau^2\left ( m_{H_d}^2+m_{L3}^2+4m_{e3}^2+4M_1^2\right )+\frac{12}{5}g_1^2\left ( a_\tau^2-2y_\tau a_\tau M_1\right )\nonumber\\
&{}+\frac{6}{5}g_1^2\sum_{i=1}^3\left [ \lambda_i^2\left ( m_{H_i^d}^2-m_{H_i^u}^2\right )+\kappa_i^2\left ( m_{\overline{D}i}^2-m_{Di}^2\right )\right ]+12g_1'^2y_b^2\left ( Q_Q^2+Q_d^2-Q_1^2\right )\times\nonumber\\
&{}\times\left ( m_{H_d}^2+m_{Q3}^2+m_{d3}^2+2M_1'^2\right )+12g_1'^2\left ( Q_Q^2+Q_d^2-Q_1^2\right )\left ( a_b^2-2y_ba_bM_1'\right )\nonumber\\
&{}-24Q_1g_1'^2y_b^2\left ( Q_1m_{H_d}^2+Q_Qm_{Q3}^2+Q_dm_{d3}^2\right )+4g_1'^2y_\tau^2\left ( Q_L^2+Q_e^2-Q_1^2\right )\times\nonumber\\
&{}\times\left ( m_{H_d}^2+m_{L3}^2+m_{e3}^2+2M_1'^2\right )+4g_1'^2\left ( Q_L^2+Q_e^2-Q_1^2\right )\left ( a_\tau^2-2y_\tau a_\tau M_1'\right )\nonumber\\
&{}-8Q_1g_1'^2y_\tau^2\left ( Q_1m_{H_d}^2+Q_Lm_{L3}^2+Q_em_{e3}^2\right )-24Q_1g_1'^2y_t^2\left ( Q_2m_{H_u}^2+Q_Qm_{Q3}^2+Q_um_{u3}^2\right )\nonumber\\
&{}+4g_1'^2\lambda^2\left ( Q_2^2+Q_S^2-Q_1^2\right )\left ( m_{H_d}^2+m_{H_u}^2+m_S^2+2M_1'^2\right )+4g_1'^2\left ( Q_2^2+Q_S^2-Q_1^2\right )\times\nonumber\\
&{}\times\left ( a_\lambda^2-2\lambda a_\lambda M_1'\right )-4Q_1g_1'^2\sum_{i=1}^3\left [ 2\lambda_i^2\left ( Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2+Q_Sm_S^2\right )\right.\nonumber\\
&{}\left.+3\kappa_i^2\left ( m_S^2+m_{Di}^2+m_{\overline{D}i}^2\right )\right ]-\frac{16}{5}g_3^2g_1^2\sum_{i=1}^3\left ( m_{Qi}^2-2m_{ui}^2+m_{di}^2+m_{\overline{D}i}^2-m_{Di}^2\right )\nonumber\\
&{}+32Q_1g_3^2g_1'^2\sum_{i=1}^3\left ( 2Q_Qm_{Qi}^2+Q_um_{ui}^2+Q_dm_{di}^2+Q_{\overline{D}}m_{\overline{D}i}^2+Q_Dm_{Di}^2\right )\nonumber\\
&{}+\frac{9}{5}g_2^2g_1^2\left [ 2\left ( M_1^2+M_1M_2+M_2^2\right )+m_{H'}^2-m_{\overline{H'}}^2-\sum_{i=1}^3\left ( m_{Qi}^2-m_{Li}^2+m_{H_i^u}^2-m_{H_i^d}^2\right )\right ]\nonumber\\
&{}+12Q_1g_2^2g_1'^2\bigg [ 2Q_1\left ( M_1'^2+M_1'M_2+M_2^2\right )+Q_{H'}m_{H'}^2+Q_{\overline{H'}}m_{\overline{H'}}^2\nonumber\\
&{}+\sum_{i=1}^3\left ( 3Q_Qm_{Qi}^2+Q_Lm_{Li}^2+Q_1m_{H_i^d}^2+Q_2m_{H_i^u}^2\right )\bigg ]+\frac{1}{25}g_1^4\bigg [ 891M_1^2+18m_{H'}^2\nonumber\\
&{}+2\sum_{i=1}^3\left ( m_{di}^2+5m_{Di}^2+m_{\overline{D}i}^2-9m_{ei}^2+9m_{H_i^d}^2+9m_{Li}^2+m_{Qi}^2+28m_{ui}^2\right )\bigg ]\nonumber\\
&{}-\frac{4}{5}g_1^2g_1'^2\bigg [ 6Q_1\big ( 3Q_d+3Q_{\overline{D}}-3Q_D+3Q_e-4Q_1+3Q_2+Q_{\overline{H'}}-Q_{H'}-3Q_L\nonumber\\
&{}+3Q_Q-6Q_u\big )\left ( M_1^2+M_1M_1'+M_1'^2\right )+3Q_{\overline{H'}}^2m_{\overline{H'}}^2-3Q_{H'}^2m_{H'}^2\nonumber\\
&{}+3\sum_{i=1}^3\big ( Q_d^2m_{di}^2+Q_{\overline{D}}^2m_{\overline{D}i}^2-Q_D^2m_{Di}^2+Q_e^2m_{ei}^2-Q_1^2m_{H_i^d}^2+Q_2^2m_{H_i^u}^2-Q_L^2m_{Li}^2\nonumber\\
&{}+Q_Q^2m_{Qi}^2-2Q_u^2m_{ui}^2\big )+3Q_1Q_{\overline{H'}}m_{\overline{H'}}^2-9Q_1Q_{H'}m_{H'}^2+Q_1\sum_{i=1}^3\bigg ( 4Q_dm_{di}^2+4Q_{\overline{D}}m_{\overline{D}i}^2\nonumber\\
&{}-8Q_Dm_{Di}^2-9Q_1m_{H_i^d}^2+3Q_2m_{H_i^u}^2-9Q_Lm_{Li}^2+5Q_Qm_{Qi}^2-20Q_um_{ui}^2\big )\bigg ]\nonumber\\
&{}+8Q_1g_1'^4\bigg [ 3Q_1M_1'^2\big ( 9Q_d^2+9Q_{\overline{D}}^2+9Q_D^2+3Q_e^2+8Q_1^2+6Q_2^2+2Q_{\overline{H'}}^2+2Q_{H'}^2+6Q_L^2\nonumber\\
&{}+18Q_Q^2+3Q_S^2+9Q_u^2\big )+2Q_{\overline{H'}}^3m_{\overline{H'}}^2+2Q_{H'}^3m_{H'}^2+\sum_{i=1}^3\big ( 3Q_d^3m_{di}^2+3Q_{\overline{D}}^3m_{\overline{D}i}^2+3Q_D^3m_{Di}^2\nonumber\\
&{}+Q_e^3m_{ei}^2+2Q_1^3m_{H_i^d}^2+2Q_2^3m_{H_i^u}^2+2Q_L^3m_{Li}^2+6Q_Q^3m_{Qi}^2+Q_S^3m_{Si}^2+3Q_u^3m_{ui}^2\big )\nonumber\\
&{}+2Q_1Q_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_1Q_{H'}m_{H'}^2+Q_1\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2\nonumber\\
&{}+2Q_1^2m_{H_i^d}^2+2Q_2^2m_{H_i^u}^2+2Q_L^2m_{Li}^2+6Q_Q^2m_{Qi}^2+Q_S^2m_{Si}^2+3Q_u^2m_{ui}^2\big )\bigg ],\label{eq:USSMmHd2BetaTwoLoop}\\

@@

&{}+2Q_2Q_{\overline{H'}}^2m_{\overline{H'}}^2+2Q_2Q_{H'}^2m_{H'}^2+Q_2\sum_{i=1}^3\big ( 3Q_d^2m_{di}^2+3Q_{\overline{D}}^2m_{\overline{D}i}^2+3Q_D^2m_{Di}^2+Q_e^2m_{ei}^2\nonumber\\
